---
title: "Getting Started with hypersonicIntercept"
author: "R. Mullen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with hypersonicIntercept}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `hypersonicIntercept` package provides tools for statistical modeling of missile interception success rates based on speed characteristics. This vignette demonstrates the basic workflow.

## Loading Data

First, load your missile launch database from an Excel file:

```{r eval=FALSE}
library(hypersonicIntercept)

data <- import_missile_data("path/to/MissileLaunchDatabase.xlsx")
head(data)
```

## Fitting Models

The package includes several pre-built logistic regression models:

### Simple Mach Model
```{r eval=FALSE}
model_mach <- fit_mach_model(data)
summary(model_mach)
```

### Hypersonic Designation Model
```{r eval=FALSE}
model_hypersonic <- fit_hypersonic_model(data)
summary(model_hypersonic)
```

### Non-linear Mach Model
```{r eval=FALSE}
model_mach_sq <- fit_mach_squared_model(data)
summary(model_mach_sq)
```

### Interaction Model
```{r eval=FALSE}
model_interaction <- fit_interaction_model(data)
summary(model_interaction)
```

## Making Predictions

Generate predictions for new speed values:

```{r eval=FALSE}
# Create a sequence of Mach speeds
new_speeds <- data.frame(Mach = seq(1, 22, by = 0.5))

# Get predicted probabilities of successful interception
predictions <- predict_interception(model_mach, new_speeds)

# View first few predictions
head(predictions)
```

## Comparing Models

Compare multiple models using AIC and BIC criteria:

```{r eval=FALSE}
comparison <- compare_models(
  model_mach,
  model_hypersonic,
  model_mach_sq,
  model_interaction
)

print(comparison)
```

The model with the lowest AIC has the best balance between fit quality and model complexity.

## Visualization

Plot the fitted model against your data:

```{r eval=FALSE}
plot_model_fit(data, model_mach, "Mach", "Mach Speed")
```

This creates a scatter plot of your observed interception outcomes with the fitted logistic curve overlaid in red.

## Workflow Summary

1. **Load data** using `import_missile_data()`
2. **Fit models** using the various `fit_*_model()` functions
3. **Compare models** using `compare_models()`
4. **Make predictions** using `predict_interception()`
5. **Visualize results** using `plot_model_fit()`

For more information, see the model diagnostics vignette and individual function documentation.
