---
title: "Getting Started with hypersonicIntercept"
author: "R. Mullen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with hypersonicIntercept}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `hypersonicIntercept` package provides tools for statistical modeling of missile interception success rates based on speed characteristics. This vignette demonstrates the basic workflow using the included sample dataset.

## Loading Data

The package includes a realistic sample dataset with 221 missile launch records:

```{r eval=FALSE}
library(hypersonicIntercept)

# Load the sample dataset
data(missile_launch_database)
head(missile_launch_database)

# Or import your own data from Excel
data <- import_missile_data("path/to/MissileLaunchDatabase.xlsx")
```

## Fitting Models

The package includes several pre-built logistic regression models, from simple to advanced:

### Simple Models
```{r eval=FALSE}
# Mach-based model
model_mach <- fit_mach_model(missile_launch_database)
summary(model_mach)

# Hypersonic designation model
model_hypersonic <- fit_hypersonic_model(missile_launch_database)
summary(model_hypersonic)
```

### Advanced Models
```{r eval=FALSE}
# Log-transformed Mach
model_log <- fit_mach_log_model(missile_launch_database)
summary(model_log)

# Polynomial Mach (non-linear)
model_poly <- fit_polynomial_mach_model(missile_launch_database, degree = 3)
summary(model_poly)

# Natural cubic splines
model_spline <- fit_spline_model(missile_launch_database, knots = 4)
summary(model_spline)

# Full additive model with interactions (best performer from research)
model_full <- fit_full_additive_model(missile_launch_database)
summary(model_full)
```

## Making Predictions

Generate predictions for new speed values:

```{r eval=FALSE}
# Create a sequence of Mach speeds
new_speeds <- data.frame(Mach = seq(1, 22, by = 1))

# Get predicted probabilities
predictions <- predict_interception(model_mach, new_speeds)
head(predictions)

# Get predictions with confidence intervals
predictions_ci <- predict_interception_ci(model_mach, new_speeds)
head(predictions_ci)
```

## Comparing Models

Compare multiple models using AIC, BIC, and other criteria:

```{r eval=FALSE}
# Compare individual models
comparison <- compare_models(
  model_mach,
  model_log,
  model_poly,
  model_full
)

print(comparison)

# Get detailed summary table
summary_table <- get_model_summary_table(
  model_mach,
  model_log,
  model_poly,
  model_full
)

print(summary_table)
```

## Model Diagnostics

Assess model quality and identify potential issues:

```{r eval=FALSE}
# Calculate diagnostic statistics
diagnostics <- calculate_model_diagnostics(model_mach)

# Identify outliers (standardized residuals > 3)
outliers <- diagnostics$outliers
print(paste("Outliers detected at indices:", paste(outliers, collapse=", ")))

# Identify influential points (high Cook's distance)
influential <- diagnostics$influential_points
print(paste("Influential points at indices:", paste(influential, collapse=", ")))
```

## Model Performance

Calculate classification performance metrics:

```{r eval=FALSE}
# Get performance metrics
performance <- calculate_model_performance(model_mach, missile_launch_database)
print(performance)

# Metrics include:
# - Accuracy: Overall proportion of correct classifications
# - Sensitivity: True positive rate (successfully intercepted)
# - Specificity: True negative rate (correctly predicted failures)
# - Precision: Positive predictive value
# - F1 Score: Harmonic mean of precision and sensitivity
```

## Visualization

Plot the fitted model against your data:

```{r eval=FALSE}
plot_model_fit(missile_launch_database, model_mach, "Mach", "Mach Speed")

# For models with multiple predictors
# For hypersonic model
plot_model_fit(missile_launch_database, model_hypersonic, 
               "Hypersonic", "Hypersonic Status")
```

## Complete Workflow Example

Here's a complete analysis pipeline:

```{r eval=FALSE}
library(hypersonicIntercept)
data(missile_launch_database)

# 1. Fit multiple candidate models
m1 <- fit_mach_model(missile_launch_database)
m2 <- fit_log_model(missile_launch_database)
m3 <- fit_full_additive_model(missile_launch_database)

# 2. Compare models
comparison <- compare_models(m1, m2, m3)
print(comparison)

# 3. Select best model
best_model <- m3  # Typically lowest AIC

# 4. Check diagnostics
diagnostics <- calculate_model_diagnostics(best_model)
cat("Outliers:", length(diagnostics$outliers), "\n")
cat("Influential points:", length(diagnostics$influential_points), "\n")

# 5. Evaluate performance
performance <- calculate_model_performance(best_model, missile_launch_database)
print(performance)

# 6. Make predictions
new_data <- data.frame(
  Mach = c(5, 10, 15, 20),
  Hypersonic = c(0, 1, 1, 1)
)
predictions <- predict_interception_ci(best_model, new_data)
print(predictions)

# 7. Visualize
plot_model_fit(missile_launch_database, best_model, "Mach", "Mach Speed")
```

## Advanced Topics

For more information on specific analyses, see:
- Model diagnostics and validation
- Handling missing data
- Feature engineering and selection
- Cross-validation strategies

For details, see function documentation: `?function_name`
